---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# whozr

 <!-- badges: start -->
[![R build status](https://github.com/simisc/whozr/workflows/R-CMD-check/badge.svg)](https://github.com/simisc/whozr/actions)
[![DOI](https://zenodo.org/badge/113995327.svg)](https://zenodo.org/badge/latestdoi/113995327)
[![Licence](https://img.shields.io/github/license/simisc/whozr)](https://github.com/simisc/whozr/blob/master/LICENSE)
[![Lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
<!-- badges: end -->

Convert raw anthropometric measurement (weight, height, length, BMI, MUAC, head circumeference, tricep skinfold and subscapular skinfold) to z-scores, using the WHO growth standards (0-5 years) and/or references (5-19 years).

Also allows the 'reverse' calculation of original anthropometry measures from z-scores (requires further testing).

## Installation

You can install whozr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("simisc/whozr")
```

## Example

```{r message=FALSE, warning=FALSE}
library(dplyr) # tibble(), %>%, mutate()
library(knitr) # kable()
library(whozr) # zwa(), zla(), zwl()
```


```{r}
tibble(sex = c("F", "M", "M", "F"),
       age_days = c(120, 310, 370, 460),
       weight_kg = c(5.98, 8.09, 8.40, 8.46),
       length_cm = c(60.2, 70.7, 72.6, 74.9)) %>%
    mutate(waz = zwa(weight_kg, age_days, sex),
           laz = zla(length_cm, age_days, sex),
           wlz = zwl(weight_kg, length_cm, sex)) %>%
    kable(digits = 3)
```

